Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-11 docs/thesis/chap-advanced_techniques.tex
work on document: added conclussions, future work, general review.

{\footnotesize
\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}c|>{\centering\arraybackslash}m{3.5cm}c|}
\hline 
\textbf{Term} & \textbf{Relative frequence} & \textbf{Term} & \textbf{Relative frequence} \\ 
\hline 
<mi>cos</mi> <mo></mo>	&0.163661208&		<mi>∞</mi>&	0.233151718\\ \hline 
<mi>cos</mi>&	0.157439621	&	<mo>→</mo> <mi>∞</mi>&	0.108867782\\ \hline 
<mo></mo>&	0.121893736&		<mo>→</mo>&	0.108017583\\ \hline 
<mi>θ</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
<mo></mo> <mi>θ</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>θ</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
<mi>cos</mi> <mo></mo> <mi>θ</mi> &	0.088535288&		<mrow> <mo>+</mo> <mi>∞</mi> </mrow>&	0.055650946\\ \hline 
<mi>sin</mi> <mo></mo>&	0.068049679&		<mo>+</mo> <mi>∞</mi>&	0.055490528\\ \hline 
<mi>sin</mi>&	0.066531563&		<mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.043459138\\ \hline 
<mrow> <mi>sin</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.032338911&		<mo>,</mo> <mi>∞</mi> & 0.021523067\\ \hline 
<mi>sin</mi> <mo></mo> <mi>θ</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
<mi>φ</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
<mi>ϕ</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
<mi></mi>&	0.018438684&		<mi>t</mi>&	0.014620022\\ \hline 
<mo></mo> <mi>ϕ</mi> & 0.017617149 & <mrow> <mo>$\pm$ </mo ><mi>∞ </mi> </mrow> & 0.014477746\\ \hline 
<mrow> <mrow> <mi>cos</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.016889963& <mo>$\pm$</mo> <mi>$\infty$</mi>& 0.014348642\\ \hline 
<mi>cos</mi> <mo></mo> <mi>ϕ</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
<mrow> <mi>cos</mi> <mo></mo> <mi>ϕ</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
<mo>φ</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
<mi>α</mi>&	0.014598769 &		<mo>∈</mo>	& 0.009871146\\ \hline

>>>>

{\footnotesize
\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}c|>{\centering\arraybackslash}m{3.5cm}c|}
\hline 
\textbf{Term} & \textbf{Relative frequence} & \textbf{Term} & \textbf{Relative frequence} \\ 
\hline 
<mi>cos</mi> <mo></mo>	&0.163661208&		<mi>∞</mi>&	0.233151718\\ \hline 
<mi>cos</mi>&	0.157439621	&	<mo>→</mo> <mi>∞</mi>&	0.108867782\\ \hline 
<mo></mo>&	0.121893736&		<mo>→</mo>&	0.108017583\\ \hline 
<mi>$\theta$</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
<mo></mo> <mi>$\theta$</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>$\theta$</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
<mi>cos</mi> <mo></mo> <mi>θ</mi> &	0.088535288&		<mrow> <mo>+</mo> <mi>∞</mi> </mrow>&	0.055650946\\ \hline 
<mi>sin</mi> <mo></mo>&	0.068049679&		<mo>+</mo> <mi>∞</mi>&	0.055490528\\ \hline 
<mi>sin</mi>&	0.066531563&		<mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.043459138\\ \hline 
<mrow> <mi>sin</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.032338911&		<mo>,</mo> <mi>∞</mi> & 0.021523067\\ \hline 
<mi>sin</mi> <mo></mo> <mi>$\theta$</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
<mi>$\phi$</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
<mi>$\Phi$</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
<mi></mi>&	0.018438684&		<mi>t</mi>&	0.014620022\\ \hline 
<mo></mo> <mi>$\Phi$</mi> & 0.017617149 & <mrow> <mo>$\pm$</mo > <mi>∞</mi> </mrow> & 0.014477746\\ \hline 
<mrow> <mrow> <mi>cos</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.016889963& <mo>$\pm$</mo> <mi>$\infty$</mi>& 0.014348642\\ \hline 
<mi>cos</mi> <mo></mo> <mi>$\Phi$</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
<mrow> <mi>cos</mi> <mo></mo> <mi>$\Phi$</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
<mo>$\phi$</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
<mi>$\alpha$</mi>&	0.014598769 &		<mo>$\in$</mo>	& 0.009871146\\ \hline

### 2014-03-11 docs/thesis/chap-cern_math_explorer.tex
work on document: added conclussions, future work, general review.

\section{Integration with Mathematica}
This section describes some aspects that had to be considered while implementing the integration with Mathematica. Our system uses the {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}. The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.

\subsubsection{Pattern Extraction}

@@

\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|}
\hline
Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
\hline
\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\

@@

\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <mi>x</mi> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>-</mo> <mrow> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mi>L</mi> </mrow> </mrow> <mo>)</mo> </mrow> </mrow> </math> }    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>+</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> </math>}     \\ 
\scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\

\label{comparison_simplification}
\end{tabular}

\subsubsection{Recursive interpretation}

@@

A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, more work is required. The demo setup employs the same dataset as used for experimentation.

>>>>

\section{Integration with Mathematica}
This section describes some aspects that had to be considered while implementing the integration with Mathematica. Our system uses the {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}. The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.
Once all the boilerplate has been written, the steps followed to define and find patterns in the expression are as follow: We import the string in MathML format through the command {\codefont ImportString["<mathmlExpression>", "MathML"]}. This creates the expression in the box form, but no further analysis is possible from this form. We then try to interpret this form into a fully Mathematica compatible expression by using {\codefont MakeExpression}

\subsubsection{Pattern Extraction}
Once the expression is created, finding a pattern is easy by using the command {\codefont Position[<variable holding the interpreted expression> , Pattern]}. A simple pattern for a quadratic expression is: {\codefont a\_.x\^{} 2 + b\_.x + c\_.}

\subsection{Cleaning of variables}
After each operation, all of the variables should be cleaned or it may lead to deadlocks, wrong results or other issues since the {\codefont MakeExpression} command also interprets the expression so if the expression is, for example {\codefont a = b + c} Mathematica remembers the assignment of the new value of {\codefont a} and uses it in further evaluations. The cleaning is done through the command {\codefont Remove["Global`*"]}

@@

\begin{longtable}{|>{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|}
\hline
\small{Original Form} & \small{{\codefont Simplify}} & \small{{\codefont FullSimplify}} \\
\hline
\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\

@@

\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <mi>x</mi> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>-</mo> <mrow> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mi>L</mi> </mrow> </mrow> <mo>)</mo> </mrow> </mrow> </math> }    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>+</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> </math>}     \\ 
\scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\
\hline
\caption{Comparison of different simplification modes}

\label{comparison_simplification}

\end{longtable}
\subsubsection{Recursive interpretation}

@@

A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, more work is required. The demo setup employs the same dataset as used for experimentation.
We include an online \LaTeX editor\cite{latex_editor} that renders the input expression as the user types it.

### 2014-03-11 docs/thesis/chap-conclusions.tex
work on document: added conclussions, future work, general review.

\chapter{Conclusions}
\label{chapter-conclusions}

>>>>

\chapter{Conclusions}
\label{chap-conclusions}

The area of Mathematical Information Retrieval is still very young and different systems, algorithms, datasets are being developed. Our work, $5e^{x+y}$, proposes a complete MIR system for a concrete digital library as the Cern Document Server. In terms of our proposed goals we can conclude:

\begin{itemize}
\item We explored and identified different tools and approaches to automatically detect and extract mathematical content from digital files. We conclude that Latexml and InftyReader are currently the best suitable set of tools to process Latex and PDF files respectively. We automatized the extraction process and incorporated it into the invenio workflow.
\item Our exploration of the extraction tools, lead us to identify the MathML format as the best format to store and process mathematical content. It is the recommended language for web documents, and the best extraction tools agree in it.
\item Once the mathematical expression is extracted and parsed to a suitable format the next step is identifying suitable features to index. We separated our features into notational and structural ones. For the first category, we developed some issues that have not yet been addressed in previous work and developed heuristics that allow to match more cases by normalizing unicode characters, grouping similar operators and expanding different numeric quantities. For the structural features, we explored the integration of a CAS to perform pattern matching and simplification of the given expression. 
\item We explored different IR frameworks and models to store and retrieve the indexed expressions and found the standard vector space model a suitable one for our needs.  
\item We implemented our system in top of the Solr/Lucene framework. We took advantage of the modular design of Lucene to structure our work in independent classes where each one has a defined role. This structure also allows to easily implement and incorporate further heuristics to handle more cases. Our system is deployed as a Solr plugin making it very easy to be used from an external application. As a final component in our system, we developed the glue code to integrate our search engine with Invenio and developed a simple to use web interface.
\item We performed different set of evaluation on our system to explore the queality of the retrieved results and the performance of our system. Our quality evaluations showed that a combination of notational and structural features allowed to achieved significantly better results. Our performance results showed that for indexing time, the extraction of structural features through the Mathematica CAS, imposes a heavy overhead of more than 10x, but as discussed previously, the extra work is worth with an improved set of results. The extra overhead at querying time is not insignificant but it is still acceptable for today's web usage standards. Our evaluation discarded the tree edit distance because the running time was 200 times than the time needed by a simple angular distance used in standard vector space model implementations, making this approach impractical for a big system.
\item Finally, during this work we identified areas of improvement which are worth looking for. This are presented in the next section.
\end{itemize}

### 2014-03-11 docs/thesis/chap-future_work.tex
added section of dlmf
more diagrams: main packages, query
work on document: added the quality results
work on document: added conclussions, future work, general review.

\chapter{Conclusions}
\label{chapter-conclusions}

>>>>

\chapter{Future work}
\label{chap-future_work}

Several different work direction were identified during the development of this work.

\section{Features extraction}
MathML specification include hundreds of different tags, which were not addressed in our work. They can affect drastically the semantic of an expression. A simple example is the fact that sometimes to stress that a variable represents a vector, it is standard to use a bold font. Also an arrow in top of a variable signifies the same. Dozens and even hundreds of this notations contain important information which is not taken into account by our system, since each of this requires some coding time and handling all of the cases is impractical. Also, there is the limitation of the extracting tools to handle complex constructs like matrices or embedded text.

\section{Data Analysis}
Different algorithms and techniques have been developed to overcome some of the shortcomings of the vector space model. Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system. During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and \cite{mallet} and Mahout. However, the tools are not yet ready for a big deployment and lots of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, and debugging and fixing code of some tools to make them work. Several times we got errors because of the in-memory implementations of the algorithms. Work on integrating the results of this techniques to the workflow of the system, can provide better results.

In our work, we explored the clustering of the expressions and managed to find a reasonable parameter k. However more insight from this should be developed and the information gained with the clustering step should be integrated in the workflow to both improve the results and the querying time.

\section{End to end system}
In our implementation, we explored and incorporated \LaTeX extraction to our system. For a full integration on CDS, PDF extraction becomes an important need since most of the records that do not come from ArXiV, do not include the source files.

### 2014-03-11 docs/thesis/chap-introduction.tex
work on document: added conclussions, future work, general review.

\begin{itemize}
\item Explore ways to automatically extract the mathematical content from a document collection
\item Investigate different approaches and formats to store mathematical expressions
\item Identify relevant features in a mathematical expression and how to use them to index equations
\item Using the created index, propose ways to efficiently retrieve relevant expressions and articles given an input query
\item Implement the previous steps into a complete system (a search engine) and integrate it into the Invenio software
\item Evaluate different approaches and the quality of the provided results
\item Identify deficiencies in our work and propose solutions and further directions
\end{itemize}

>>>>

\begin{itemize}
\item Explore ways to automatically extract the mathematical content from a document collection
\item Investigate different approaches and formats to store mathematical expressions
\item Identify relevant features in a mathematical expression 
\item Explore ways to efficiently store and retrieve the set of features
\item Implement the previous steps into a complete system (a search engine) and integrate it into the Invenio software
\item Evaluate different approaches and the quality of the provided results
\item Identify deficiencies in our work and propose solutions and further directions
\end{itemize}

### 2014-03-11 docs/thesis/chap-related_work.tex
work on document: added conclussions, future work, general review.

>>>>

\subsection{WikiMirs}
WikiMirs\cite{wikimirs} is a system that, as EgoMath, allows to find relevant Wikipedia entries by providing mathematical expression in \LaTeX. It combines the information about the semantic tree with the layout tree of a given expression and uses a similar approach to index different generalization levels.
